Two Problems for Sophistication

### 2015-01-21 Facticity/Facticity/paper.tex
...

(1) Let $f$ be any function in the range of $D$, and $x$ its output. Then $\min\{|p|:\psi_{D(p)}=f\}=\min\{|\bar\imath q|:\psi_i(q)=x\}=K(x)\le K(f)+c$. (2) On the one hand $L^{\M',\psi}(x)\le K(f)+|\epsilon|\le K(x)+c$. On the other hand, $L^{\M,\psi}(x)$ is an effective description of $x$, so $K(x)$ is at most a constant larger. Together, these inequalities establish the second condition.

Now, by Lemma~\ref{lemma:thecoolone} there is an enumeration $\phi_1,\phi_2,\ldots$ such that $S^{\M,\phi}(x)=|\bar 0|+S^{\M',\psi}(x)$. We observed that $|K(f)-K(x)|\le c$ for any $f\in\M'$, so $S^{\M',\psi}(x)\ge K(x)+c$. This proves the lemma.
\end{proof}
\subsection{Underfitting}

@@

\begin{proof}
Let $D$ be a prefix function as in Lemma~\ref{lemma:thecoolone} such that it returns the index of $u$ for the argument $\epsilon$ and $\infty$ for any other argument. That is, $\M' = \{u\}$. This construction satisfies the conditions 1 and 2 from Lemma~\ref{lemma:thecoolone}; invoking it we find that there exists an acceptable numbering for which $\s_\M(x) = \s_{\M'}(x) + c$. Since $\M'$ contains only a single model, $\s_{\M'}$ is constant.
\end{proof}

@@

Note that we favoured brevity of the proof over the strength of the bounds: the multiplicative constant $1/6$ can be improved with a more detailed treatment.

@@

Let $D$ be a prefix function with $D(\epsilon) = u$. We can instantiate Lemma~\ref{lemma:thecoolone} with $D$, $\M' = \{\phi_u\}$ and $X = \{x : d^\C_c(x) \leq A(C(x))\}$. This tells us that there exists a numbering for which $\s^\T(x) = \s^{\M'}(x) + |\bar0| \leq c$ for all $x \in X$.
\end{proof}

>>>>

(1) Let $f$ be any function in the range of $D$, and $x$ its output. Then $\min\{|p|:\psi_{D(p)}=f\}=\min\{|\bar\imath q|:\phi_i(q)=x\}=C^{\K}(x) \le C^{\K}(f)+c$. (2) On the one hand $C^{\M',\psi}(x)\le C^\K(f)+|\epsilon|\le C^\K(x)+c$. On the other hand, $C^{\M,\psi}(x)$ is an effective description of $x$, so $C^{\K}(x)$ is at most a constant larger. Together, these inequalities establish the second condition.

Now, by Lemma~\ref{lemma:thecoolone} there is an numbering $\psi_1,\psi_2,\ldots$ such that $\s^{\M,\phi}(x)=|\bar 0|+S^{\M',\psi}(x)$. We observed that $|C^{\K}(f)-C^{\K}(x)|\le c$ for any $f\in\M'$, so $\s^{\M',\psi}(x)\ge C^{\K}(x)-c$. This proves the lemma.
\end{proof}
\subsection{Underfitting}

@@

\begin{proof}
Let $D$ be a prefix function as in Lemma~\ref{lemma:thecoolone} such that it returns the index of $u$ for the argument $\epsilon$ and $\infty$ for any other argument. That is, $\M' = \{u\}$. This construction satisfies the conditions 1 and 2 from Lemma~\ref{lemma:thecoolone}; invoking it we find that there exists an acceptable numbering $\psi$ for which $\s^{\M,\psi}(x) = \s^{\M', phi}(x) + c$. Since $\M'$ contains only a single model, $\s_{\M',\phi}(x)$ is constant.
\end{proof}

@@

Note that we favored brevity of the proof over the strength of the bounds: the multiplicative constant $1/6$ can be improved with a more detailed treatment.

@@

Let $D$ be a prefix function with $D(\epsilon) = u$. We can instantiate Lemma~\ref{lemma:thecoolone} with $D$, $\M' = \{\phi_u\}$ and $X = \{x : d^{\C,c}(x) \leq A(C(x))\}$. This tells us that there exists a numbering for which $\s^\T(x) = \s^{\M'}(x) + |\bar0| \leq c$ for all $x \in X$.
\end{proof}
